---
title: "CBW - IATH"
output: html_document
---

## Association Rule analysis

```{r data reading,echo=FALSE}
suppressMessages( library(dplyr))
suppressMessages(library(ggplot2))

### Loading the data
load("text_data_sent.Rdata")

bess <- read.csv("CBW_Bess_tags_final.csv", stringsAsFactors = FALSE)

#"bio03_a626" "bio22_a628" "bio25_a628"
bess_title <- unique(bess[c("biographyID","collectionID","author","personaName")])
names(bess_title)[names(bess_title) == "collectionID"] <- "CollectionID"
names(bess_title)[names(bess_title) == "biographyID"] <- "BiographyID"
bess_title$key <- paste0(bess_title$CollectionID,"_",bess_title$BiographyID)

### Creating a unique id

text_data_sent$key <- paste0(text_data_sent$CollectionID,"_",text_data_sent$BiographyID)

avg_sentiment <- group_by(text_data_sent,key) %>% 
                  summarize(average_score = mean(score, na.rm = TRUE)) %>%
                    arrange(average_score)

avg_sentiment <- suppressMessages(left_join(avg_sentiment,bess_title))

```

#### Top 5 Authors


```{r Top Authors, echo=FALSE}

### Top Authors 

top_authors <-
bess_title %>% group_by(author) %>% summarise(count = n()) %>%
  arrange(desc(count)) %>% head(6) %>% filter(author != "Unknown")

top_authors$author
```

##### Sentiment across Narrative time
```{r Sentiment pattern across paragraphs, echo = FALSE}

text_all <- suppressMessages( left_join(text_data_sent,bess_title))

ggplot(data = filter(text_all, author %in% top_authors$author)
       , aes(x = ParagraphNo, y = score, col = author)) + geom_line()+ scale_fill_continuous(guide = guide_legend()) +
    theme(legend.position="bottom")


```

#### Standardizing the time line

Instead of having the absolute count of the paragraph, we can having the time normalized between 0 and 1. This will enable us to compare different biographies irrespective of their paragraph length


#### Overall analysis for all the Authors
```{r Overall analysis, echo = FALSE}

max_para_no <- group_by(text_all,CollectionID,BiographyID) %>% summarise(max(ParagraphNo))


text_all <- suppressMessages(left_join( text_all,max_para_no))
text_all$time <- text_all$ParagraphNo/text_all$`max(ParagraphNo)`



overall <- group_by(text_all,time) %>% summarise(score = mean(score))

ggplot(data =overall
       , aes(x = time, y = score)) + geom_line()



```


#### Sentiment across Narrative time - Standardized for Top Authors
```{r Sentiment std pattern across paragraphs, echo = FALSE}



ggplot(data = filter(text_all, author %in% top_authors$author)
       , aes(x = time, y = score, col = author)) + geom_point() +
  scale_fill_continuous(guide = guide_legend()) +
    theme(legend.position="bottom")


```

#### Sentiment across Narrative time - Standardized for Top Persona
```{r Sentiment Persona, echo = FALSE}
top_persona <-
  text_all %>% group_by_("personaName") %>% summarise(count = n()) %>%
  arrange(desc(count)) %>% head(10) %>% filter(personaName != "Unknown")

#top_persona$personaName
pesona_names <- top_persona$personaName[1:5]


ggplot(data = filter(text_all, personaName %in% pesona_names)
       , aes(x = time, y = score, col = personaName)) + geom_point() +
  scale_fill_continuous(guide = guide_legend()) +
    theme(legend.position ="bottom")


```
\n \n



#### Sentiment across Narrative time - Sister Dora

```{r Sentiment Persona 1, echo = FALSE}

pesona_names <- top_persona[1,]


ggplot(data = filter(text_all, personaName %in% pesona_names)
       , aes(x = time, y = score, col = personaName)) + geom_point() +
  scale_fill_continuous(guide = guide_legend()) +
    theme(legend.position ="bottom")

```


#### Sentiment across Narrative time - Agnes Weston

```{r Sentiment Persona 2, echo = FALSE}

pesona_names <- top_persona[3,]

ggplot(data = filter(text_all, personaName %in% pesona_names)
       , aes(x = time, y = score, col = personaName)) + geom_point() +
  scale_fill_continuous(guide = guide_legend()) +
    theme(legend.position ="bottom")

```

#### Sentiment Distribution

```{r Sentiment dist, echo = FALSE}


text_data_sent$sentiment <- as.character(text_data_sent$sentiment)
text_data_sent_withoutNULL <- text_data_sent %>% filter(sentiment != "NULL")


ggplot(data.frame(table(text_data_sent_withoutNULL$sentiment)),aes(x = Var1,y=Freq)) + geom_bar(stat = "identity") + xlab("Sentiment") +
    theme(legend.position ="bottom")




```

#### Sentiment Distribution Across Personas

```{r Sentiment dist 2, echo = FALSE}


ggplot(data = filter(text_all, personaName %in% top_persona$personaName),
       aes(x = reorder(personaName, ParagraphNo) , y = ParagraphNo , fill = sentiment)) + 
  geom_bar(stat = "identity") + 
  xlab("Personas")+
    theme(legend.position ="bottom")



```


#### Sentiment changes for Authors across time - Mean

```{r Sentiment change, echo = FALSE}

text_all$time_slot <- cut(text_all$time,seq(0,1,0.05))
heat_map_time_slot <- group_by(text_all,author,time_slot) %>% 
              summarize(score_mean = mean(score,na.rm = TRUE))

ggplot(data = heat_map_time_slot,
       #, aes(x = time, y = score, col = author)) +
  aes(x = author, y = time_slot,fill = score_mean)) + geom_tile()+
  scale_fill_gradient(low = "red", high = "green")    +
    theme(legend.position ="bottom")
  


```



#### Sentiment changes for Authors across time

```{r AUTHORS, echo = TRUE}

sort(unique(text_all$author))


```


#### Sentiment changes for Authors across time

```{r Similar authors, echo = F}

#### Ordering by positive and negative authors
library(stringdist)


authors <- sort(unique(text_all$author))
author_list <- list()

for(each_authors in authors){
  authors_check <- authors[!authors %in% each_authors]
  dist_vals <- stringdist(each_authors,authors_check)
  
  author_list[[each_authors]] <- authors_check[which(dist_vals < 7)]
  
  
}


```




#### Similar Authors

```{r similar authors, echo = F}

#### Ordering by positive and negative authors
author_list[unlist(lapply(author_list,function(x)length(x)>0))]

```